---
title: "ImsDataTransfer Simulation"
author: "Peter von Rohr"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

## Disclaimer
This document contains a short `How-To` for using this package to simulate composite milk record data.

## Introduction
Composite milk record data are simulated using the R6 class `R6ClassCompositeMilkRecord`. Objects of `R6ClassCompositeMilkRecord` consist of the following components.

- milkYield
- fatPercent
- proteinPercent
- sccValue
- ureaContent
- lactoseContent


## Simulate a composite milk record
A composite milk record can be simulated using the method `sampleUnifRecord()` of `R6ClassCompositeMilkRecord`. When creating an instance of `R6ClassCompositeMilkRecord` all the components are initialized. The method `sampleUnifRecord()` generates values for each of the components. The result of simulating one composite milk record can be shown as follows.

```{r SimulateCompositeMilkRecord}
### # set seed for reproducibillity
set.seed(1234)
### # instatiate a composite milk object
r6objComMilkRec <- ImsDataTransferSimulation::R6ClassCompositeMilkRecord$new()
### # simulate
r6objComMilkRec$sampleUnifRecord()
### # show the result
cat("Simulation result:\n", r6objComMilkRec$toTsvString(), "\n", sep = "")
```

The above shown record can also be written to a file using method `writeTsvStringToFile()`. 

```{r WriteResultToFile}
r6objComMilkRec$writeTsvStringToFile()
```

